``` {.r}
##Load neccessary packages
#library(rlang)
#install.packages("scales")
#install.packages("https://cran.r-project.org/src/contrib/Archive/rlang/rlang_0.4.7.tar.gz", repo=NULL, type="source")
#library(rlang)
#library(scales)
library(tidyverse) # metapackage with lots of helpful functions
```

```{r}

```

```{r}

```

    ## Error in library(tidyverse): there is no package called 'tidyverse'

``` {.r}
library(reshape2)
#install.packages("ggrepel") 
library(ggrepel)
library(plotly)
```

    ## 
    ## Attaching package: 'plotly'

    ## The following object is masked from 'package:ggplot2':
    ## 
    ##     last_plot

    ## The following object is masked from 'package:stats':
    ## 
    ##     filter

    ## The following object is masked from 'package:graphics':
    ## 
    ##     layout

``` {.r}
library(lubridate)
```

    ## 
    ## Attaching package: 'lubridate'

    ## The following objects are masked from 'package:base':
    ## 
    ##     date, intersect, setdiff, union

``` {.r}
library(data.table)
```

    ## data.table 1.14.0 using 4 threads (see ?getDTthreads).  Latest news: r-datatable.com

    ## 
    ## Attaching package: 'data.table'

    ## The following objects are masked from 'package:lubridate':
    ## 
    ##     hour, isoweek, mday, minute, month, quarter, second, wday, week, yday, year

    ## The following objects are masked from 'package:reshape2':
    ## 
    ##     dcast, melt

``` {.r}
library(recommenderlab)
```

    ## Error in library(recommenderlab): there is no package called 'recommenderlab'

``` {.r}
library(reshape2)

options(warn=-1)

NetflixDF <-  read.csv(file = "C:/Users/Soumy/Desktop/DPA/netflix/netflix_titles.csv", na.strings = c("NA", ""), stringsAsFactors=F)
```

    ## Error in file(file, "rt"): cannot open the connection

``` {.r}
##Fetch the weighted average votes/ratings of the movies from imdb for netflix

RatingsIMDB=fread("C:/Users/Soumy/Desktop/DPA/netflix/IMDb ratings.csv", select = c("weighted_average_vote"))
TitlesIMDB=fread("C:/Users/Soumy/Desktop/DPA/netflix/IMDb movies.csv", select = c('title','year','genre','reviews_from_users'))


IMDBdf = data.frame(RatingsIMDB, TitlesIMDB)
head(IMDBdf,5)
```

    ## data frame with 0 columns and 0 rows

``` {.r}
#drop duplicated rows based on the title, Release Year, Rating
IMDBdf=distinct(IMDBdf,title,year,weighted_average_vote,genre, .keep_all= TRUE)
```

    ## Error: `distinct()` must use existing variables.
    ## x `title` not found in `.data`.
    ## x `year` not found in `.data`.
    ## x `weighted_average_vote` not found in `.data`.
    ## x `genre` not found in `.data`.

``` {.r}
IMDBdf %>% drop_na("weighted_average_vote")
```

    ## Error in drop_na(., "weighted_average_vote"): could not find function "drop_na"

``` {.r}
library(dplyr)
```

    ## 
    ## Attaching package: 'dplyr'

    ## The following objects are masked from 'package:data.table':
    ## 
    ##     between, first, last

    ## The following object is masked from 'package:car':
    ## 
    ##     recode

    ## The following objects are masked from 'package:stats':
    ## 
    ##     filter, lag

    ## The following objects are masked from 'package:base':
    ## 
    ##     intersect, setdiff, setequal, union

``` {.r}
###Join netflix and imdb dataset
jointDF=inner_join(NetflixDF, IMDBdf, by = c("title"))
```

    ## Error in inner_join(NetflixDF, IMDBdf, by = c("title")): object 'NetflixDF' not found

``` {.r}
head(jointDF,1)
```

    ## Error in head(jointDF, 1): object 'jointDF' not found

``` {.r}
(dim(jointDF))
```

    ## Error in eval(expr, envir, enclos): object 'jointDF' not found

``` {.r}
#number of missing values for each variable for NetflixDF
data.frame("variable"=c(colnames(NetflixDF)), "missing values"=sapply(NetflixDF, function(x) sum(is.na(x))), row.names=NULL)
```

    ## Error in is.data.frame(x): object 'NetflixDF' not found

``` {.r}
NetflixDF$date_added <- as.Date(NetflixDF$date_added, format = "%B %d, %Y")
```

    ## Error in as.Date(NetflixDF$date_added, format = "%B %d, %Y"): object 'NetflixDF' not found

``` {.r}
#function to find a mode
getmode <- function(v) {
   unique_mode <- unique(v)
   unique_mode[which.max(tabulate(match(v, unique_mode)))]
}

###Fill by mode
NetflixDF$rating[is.na(NetflixDF$rating)] <- getmode(NetflixDF$rating)
```

    ## Error in unique(v): object 'NetflixDF' not found

``` {.r}
#drop duplicated rows based on the title, country, type and release_year
NetflixDF=distinct(NetflixDF,title,country,type,release_year, .keep_all= TRUE)
```

    ## Error in distinct(NetflixDF, title, country, type, release_year, .keep_all = TRUE): object 'NetflixDF' not found

``` {.r}
Type_amount <- NetflixDF %>% group_by(type) %>% summarise(
  count = n()
)
```

    ## Error in group_by(., type): object 'NetflixDF' not found

``` {.r}
fig1 <- plot_ly(Type_amount, labels = ~type, values = ~count, type = 'pie', marker = list(colors = c("#9467bd", "#1f77b4")))
```

    ## Error in is.data.frame(data): object 'Type_amount' not found

``` {.r}
fig1 <- fig1 %>% layout(title = 'Amount Of Netflix Content By Type')
```

    ## Error in layout(., title = "Amount Of Netflix Content By Type"): object 'fig1' not found

``` {.r}
fig1
```

    ## Error in eval(expr, envir, enclos): object 'fig1' not found

``` {.r}
s <- strsplit(NetflixDF$country, split = ", ")
```

    ## Error in strsplit(NetflixDF$country, split = ", "): object 'NetflixDF' not found

``` {.r}
Total_titles_countries <- data.frame(type = rep(NetflixDF$type, sapply(s, length)), country = unlist(s))
```

    ## Error in data.frame(type = rep(NetflixDF$type, sapply(s, length)), country = unlist(s)): object 'NetflixDF' not found

``` {.r}
Total_titles_countries$country <- as.character(gsub(",","",Total_titles_countries$country))
```

    ## Error in is.factor(x): object 'Total_titles_countries' not found

``` {.r}
country_amount <- na.omit(Total_titles_countries) %>%
  group_by(country, type) %>%
  summarise(count = n())
```

    ## Error in na.omit(Total_titles_countries): object 'Total_titles_countries' not found

``` {.r}
w <- reshape(data=data.frame(country_amount),idvar="country",
                          v.names = "count",
                          timevar = "type",
                          direction="wide") %>% arrange(desc(count.Movie)) %>%
                          top_n(10)
```

    ## Error in data.frame(country_amount): object 'country_amount' not found

``` {.r}
names(w)[2] <- "count_movie"
```

    ## Error in names(w)[2] <- "count_movie": object 'w' not found

``` {.r}
names(w)[3] <- "count_tv_show"
```

    ## Error in names(w)[3] <- "count_tv_show": object 'w' not found

``` {.r}
w <- w[order(desc(w$count_movie+w$count_tv_show)),] 
```

    ## Error in eval(expr, envir, enclos): object 'w' not found

``` {.r}
fig <- plot_ly(w, x = w$country, y = ~count_movie, type = 'bar', name = 'Movie', marker = list(color = '#9467bd'))
```

    ## Error in is.data.frame(data): object 'w' not found

``` {.r}
fig <- fig %>% add_trace(y = ~count_tv_show, name = 'TV Show',marker = list(color = '#1f77b4'))
```

    ## Error in add_data(p, data): object 'fig' not found

``` {.r}
fig <- fig %>% layout(xaxis=list(categoryorder = "array", categoryarray = w$country, title="Country"), yaxis = list(title = 'Amount of content'), barmode = 'stack', title = 'Top Countries distribution of the produced content')
```

    ## Error in layout(., xaxis = list(categoryorder = "array", categoryarray = w$country, : object 'fig' not found

``` {.r}
fig
```

    ## Error in eval(expr, envir, enclos): object 'fig' not found

``` {.r}
unique_vals <- apply(NetflixDF, MARGIN = 2, FUN = function(x) length(unique(x)))
```

    ## Error in apply(NetflixDF, MARGIN = 2, FUN = function(x) length(unique(x))): object 'NetflixDF' not found

``` {.r}
unique_vals <- data.frame(Columns = names(unique_vals), UniqueCounts = unique_vals, stringsAsFactors = F)
```

    ## Error in data.frame(Columns = names(unique_vals), UniqueCounts = unique_vals, : object 'unique_vals' not found

``` {.r}
options(repr.plot.width=10, repr.plot.height=8)
unique_vals %>% ggplot(aes(x = Columns, y = UniqueCounts)) + 
                       geom_bar(stat = 'identity',fill="#56B4E9") + 
                       scale_x_discrete(limits = colnames(NetflixDF)) + 
                       geom_hline(yintercept = nrow(NetflixDF)) + 
                       geom_label(aes(x = 4, y = nrow(NetflixDF), label = 'Number of rows in the input'), size = 5) + theme_bw()
```

    ## Error in ggplot(., aes(x = Columns, y = UniqueCounts)): object 'unique_vals' not found

``` {.r}
DF_bydate <- NetflixDF %>% group_by(date_added,type) %>% summarise(addedToday = n()) %>% 
            ungroup() %>% group_by(type) %>% mutate(Total_Number_of_Shows = cumsum(addedToday), label = if_else(date_added == max(date_added,na.rm = T), as.character(type), NA_character_))
```

    ## Error in group_by(., date_added, type): object 'NetflixDF' not found

``` {.r}
DF_bydateTotal <- NetflixDF %>% group_by(date_added) %>% summarise(added_today = n()) %>% 
  mutate(total_number_of_content = cumsum(added_today), type = "Total")
```

    ## Error in group_by(., date_added): object 'NetflixDF' not found

``` {.r}
DF_bydate <- NetflixDF %>% group_by(date_added,type) %>% summarise(added_today = n()) %>% 
            ungroup() %>% group_by(type) %>% mutate(total_number_of_content = cumsum(added_today))
```

    ## Error in group_by(., date_added, type): object 'NetflixDF' not found

``` {.r}
TotalDF<- rbind(as.data.frame(DF_bydateTotal), as.data.frame(DF_bydate))
```

    ## Error in as.data.frame(DF_bydateTotal): object 'DF_bydateTotal' not found

``` {.r}
fig4 <- plot_ly(TotalDF, x = ~date_added, y = ~total_number_of_content, color = ~type, type = 'scatter', mode = 'lines', colors=c("#9467bd","#ff7f0e","#1f77b4")) 
```

    ## Error in is.data.frame(data): object 'TotalDF' not found

``` {.r}
fig4 <- fig4 %>% layout(yaxis = list(title = 'Total number of Shows or Movies'), xaxis = list(title = 'Date content was added'), title="Amout Of Content As A Function Of Time")
```

    ## Error in layout(., yaxis = list(title = "Total number of Shows or Movies"), : object 'fig4' not found

``` {.r}
fig4
```

    ## Error in eval(expr, envir, enclos): object 'fig4' not found

``` {.r}
Total_Rating_DF <- NetflixDF %>% group_by(rating) %>% summarise(count = n())
```

    ## Error in group_by(., rating): object 'NetflixDF' not found

``` {.r}
fig6 <- plot_ly(Total_Rating_DF, labels = ~rating, values = ~count, type = 'pie')
```

    ## Error in is.data.frame(data): object 'Total_Rating_DF' not found

``` {.r}
fig6 <- fig6 %>% layout(title = 'Amount Of Content By Rating')
```

    ## Error in layout(., title = "Amount Of Content By Rating"): object 'fig6' not found

``` {.r}
fig6
```

    ## Error in eval(expr, envir, enclos): object 'fig6' not found

``` {.r}
topGenr <- strsplit(NetflixDF$listed_in, split = ",")
```

    ## Error in strsplit(NetflixDF$listed_in, split = ","): object 'NetflixDF' not found

``` {.r}
listedTitles <- data.frame(type = rep(NetflixDF$type, sapply(topGenr, length)), listed_in = unlist(topGenr))
```

    ## Error in data.frame(type = rep(NetflixDF$type, sapply(topGenr, length)), : object 'NetflixDF' not found

``` {.r}
listedTitles$listed_in <- as.character(gsub(",","",listedTitles$listed_in))
```

    ## Error in is.factor(x): object 'listedTitles' not found

``` {.r}
ListedtotalDF <- listedTitles %>% group_by(listed_in) %>% summarise(count = n()) %>%
  arrange(desc(count)) %>% top_n(20)
```

    ## Error in group_by(., listed_in): object 'listedTitles' not found

``` {.r}
fig7 <- plot_ly(ListedtotalDF, x = ~listed_in, y = ~count, type = 'bar', marker = list(color = 'palegreen'))
```

    ## Error in is.data.frame(data): object 'ListedtotalDF' not found

``` {.r}
fig7 <- fig7 %>% layout(xaxis=list(categoryorder = "array", categoryarray = ListedtotalDF$listed_in, title="Genre"), yaxis = list(title = 'Count'), title="20 Top Genres On Netflix")
```

    ## Error in layout(., xaxis = list(categoryorder = "array", categoryarray = ListedtotalDF$listed_in, : object 'fig7' not found

``` {.r}
fig7
```

    ## Error in eval(expr, envir, enclos): object 'fig7' not found

``` {.r}
Country_moviesbyduration<-na.omit(NetflixDF[NetflixDF$type=="Movie",][,c("country", "duration")])
```

    ## Error in na.omit(NetflixDF[NetflixDF$type == "Movie", ][, c("country", : object 'NetflixDF' not found

``` {.r}
countrydur_s <- strsplit(Country_moviesbyduration$country, split = ", ")
```

    ## Error in strsplit(Country_moviesbyduration$country, split = ", "): object 'Country_moviesbyduration' not found

``` {.r}
Country_moviesbydurationTotal <- data.frame(duration = rep(Country_moviesbyduration$duration, sapply(countrydur_s, length)), country = unlist(countrydur_s))
```

    ## Error in data.frame(duration = rep(Country_moviesbyduration$duration, : object 'Country_moviesbyduration' not found

``` {.r}
Country_moviesbydurationTotal$duration <- as.numeric(gsub(" min","", Country_moviesbydurationTotal$duration))
```

    ## Error in is.factor(x): object 'Country_moviesbydurationTotal' not found

``` {.r}
Subset_Country_moviesbydurationTotal<-Country_moviesbydurationTotal[Country_moviesbydurationTotal$country %in% c("United States", "India", "United Kingdom", "Canada", "France", "Japan", "Spain", "South Korea", "Mexico", "Australia", "Taiwan"),]
```

    ## Error in eval(expr, envir, enclos): object 'Country_moviesbydurationTotal' not found

``` {.r}
fig8 <- plot_ly(Subset_Country_moviesbydurationTotal, y = ~duration, color = ~country, type = "box")
```

    ## Error in is.data.frame(data): object 'Subset_Country_moviesbydurationTotal' not found

``` {.r}
fig8 <- fig8 %>% layout(xaxis=list(title="Country"), yaxis = list(title = 'Duration (in min)'), 
        title="Box-Plots Of Movie Duration In Top 11 Countries")
```

    ## Error in layout(., xaxis = list(title = "Country"), yaxis = list(title = "Duration (in min)"), : object 'fig8' not found

``` {.r}
fig8
```

    ## Error in eval(expr, envir, enclos): object 'fig8' not found

``` {.r}
ShowCategoriesDF <- NetflixDF %>% 
                        select(c('show_id','type','listed_in')) %>% 
                        separate_rows(listed_in, sep = ',') %>%
                        rename(Show_Category = listed_in)
```

    ## Error in separate_rows(., listed_in, sep = ","): could not find function "separate_rows"

``` {.r}
ShowCategoriesDF$Show_Category <- trimws(ShowCategoriesDF$Show_Category)
```

    ## Error in is.factor(x): object 'ShowCategoriesDF' not found

``` {.r}
head(ShowCategoriesDF)
```

    ## Error in head(ShowCategoriesDF): object 'ShowCategoriesDF' not found

``` {.r}
ShowCategoriesDF %>% mutate(Show_Category = fct_infreq(Show_Category)) %>% 
        ggplot(aes(x = Show_Category)) + 
            geom_bar() + scale_x_discrete() + facet_wrap(~type, scales = 'free_x') + 
            theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme() + coord_cartesian(xlim = c(1,20))
```

    ## Error in mutate(., Show_Category = fct_infreq(Show_Category)): object 'ShowCategoriesDF' not found

``` {.r}
UniqCategoriesDF <- ShowCategoriesDF %>% group_by(type,Show_Category) %>%  summarise()
```

    ## Error in group_by(., type, Show_Category): object 'ShowCategoriesDF' not found

``` {.r}
MoviesCategories_CorrDF <- data.frame(expand_grid(type = 'Movie', 
                                             Category1 = subset(UniqCategoriesDF, type == 'Movie')$Show_Category,
                                             Category2 = subset(UniqCategoriesDF, type == 'Movie')$Show_Category))
```

    ## Error in expand_grid(type = "Movie", Category1 = subset(UniqCategoriesDF, : could not find function "expand_grid"

``` {.r}
TVCategories_CorrDF <-      data.frame(expand_grid(type = 'TV Show', 
                                             Category1 = subset(UniqCategoriesDF, type == 'TV Show')$Show_Category,
                                             Category2 = subset(UniqCategoriesDF, type == 'TV Show')$Show_Category))
```

    ## Error in expand_grid(type = "TV Show", Category1 = subset(UniqCategoriesDF, : could not find function "expand_grid"

``` {.r}
Categories_CorrDF <- rbind(MoviesCategories_CorrDF,TVCategories_CorrDF)
```

    ## Error in rbind(MoviesCategories_CorrDF, TVCategories_CorrDF): object 'MoviesCategories_CorrDF' not found

``` {.r}
Categories_CorrDF$matched_count <- apply(Categories_CorrDF, MARGIN = 1,FUN = function(x) {
                                            length(intersect(subset(ShowCategoriesDF, type == x['type'] & Show_Category == x['Category1'])$show_id,
                                            subset(ShowCategoriesDF, type == x['type'] & Show_Category == x['Category2'])$show_id))})
```

    ## Error in apply(Categories_CorrDF, MARGIN = 1, FUN = function(x) {: object 'Categories_CorrDF' not found

``` {.r}
Categories_CorrDF <- subset(Categories_CorrDF, (as.character(Category1) < as.character(Category2)) & (matched_count > 0))
```

    ## Error in subset(Categories_CorrDF, (as.character(Category1) < as.character(Category2)) & : object 'Categories_CorrDF' not found

``` {.r}
options(repr.plot.width=20, repr.plot.height=10)           

ggplot(subset(Categories_CorrDF, type == 'Movie'), aes(x = Category1, y = Category2, fill = matched_count)) + 
        geom_tile() + facet_wrap( ~type, scales = 'free') + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + scale_fill_distiller(palette = "Spectral") + 
           theme(legend.text = element_text(size = 14), legend.title = element_text(size = 20))
```

    ## Error in subset(Categories_CorrDF, type == "Movie"): object 'Categories_CorrDF' not found

``` {.r}
ggplot(subset(Categories_CorrDF, type == 'TV Show'), aes(x = Category1, y = Category2, fill = matched_count)) + 
        geom_tile() + facet_wrap( ~type, scales = 'free') + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + scale_fill_distiller(palette = "Spectral") + 
            theme(legend.text = element_text(size = 14), legend.title = element_text(size = 16))
```

    ## Error in subset(Categories_CorrDF, type == "TV Show"): object 'Categories_CorrDF' not found

``` {.r}
###Separating the list of comma separated actor lists

NetflixDF %>% select(c('show_id','cast','director')) %>% 
        gather(key = 'role', value = 'person', cast, director) %>% 
             filter(person != "") %>% separate_rows(person, sep = ',') -> Show_personDF
```

    ## Error in separate_rows(., person, sep = ","): could not find function "separate_rows"

``` {.r}
Show_personDF$person <- trimws(Show_personDF$person)
```

    ## Error in is.factor(x): object 'Show_personDF' not found

``` {.r}
head(Show_personDF)
```

    ## Error in head(Show_personDF): object 'Show_personDF' not found

``` {.r}
FreqPersonDF<- Show_personDF %>% group_by(person,role) %>% 
                    summarise(count = n()) %>% arrange(desc(count))
```

    ## Error in group_by(., person, role): object 'Show_personDF' not found

``` {.r}
FreqPersonDF %>% group_by(role) %>% top_n(10,count) %>% ungroup() %>% ggplot(aes(x = fct_reorder(person,count,.desc = T), y = count, fill = role)) + 
            geom_bar(stat = 'identity') + scale_x_discrete() + facet_wrap(~role, scales = 'free_x') + 
            theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(legend.position = 'none') + labs(x = 'Name of the actor / director')
```

    ## Error in group_by(., role): object 'FreqPersonDF' not found

``` {.r}
topDir <- strsplit(NetflixDF$director, split = ", ")
```

    ## Error in strsplit(NetflixDF$director, split = ", "): object 'NetflixDF' not found

``` {.r}
DirectorTitles <- data.frame(type = rep(NetflixDF$type, sapply(topDir, length)), director = unlist(topDir))
```

    ## Error in data.frame(type = rep(NetflixDF$type, sapply(topDir, length)), : object 'NetflixDF' not found

``` {.r}
DirectorTitles$director <- as.character(gsub(",","",DirectorTitles$director))
```

    ## Error in is.factor(x): object 'DirectorTitles' not found

``` {.r}
DirectorTitles<-na.omit(DirectorTitles) %>%  group_by(director)  %>% summarise(count = n()) %>% arrange(desc(count)) %>% top_n(10)
```

    ## Error in na.omit(DirectorTitles): object 'DirectorTitles' not found

``` {.r}
DirectorTitles<-as.data.frame(DirectorTitles)
```

    ## Error in as.data.frame(DirectorTitles): object 'DirectorTitles' not found

``` {.r}
DirectorTitles
```

    ## Error in eval(expr, envir, enclos): object 'DirectorTitles' not found

``` {.r}
dir_<-ggplot(data=DirectorTitles, aes(x=director, y=count)) +
  geom_bar(stat="identity", fill="rosybrown")+
  geom_text(aes(label=count), vjust=1.6, color="white", size=5.5)+
  theme_classic()
```

    ## Error in ggplot(data = DirectorTitles, aes(x = director, y = count)): object 'DirectorTitles' not found

``` {.r}
dir_
```

    ## Error in eval(expr, envir, enclos): object 'dir_' not found

``` {.r}
topActr <- strsplit(NetflixDF[NetflixDF$country=="United States",]$cast, split = ", ")
```

    ## Error in strsplit(NetflixDF[NetflixDF$country == "United States", ]$cast, : object 'NetflixDF' not found

``` {.r}
ActorTitles <- data.frame(type = rep(NetflixDF[NetflixDF$country=="United States",]$type, sapply(topActr, length)), actor = unlist(topActr))
```

    ## Error in data.frame(type = rep(NetflixDF[NetflixDF$country == "United States", : object 'NetflixDF' not found

``` {.r}
ActorTitles$actor <- as.character(gsub(",","",ActorTitles$actor))
```

    ## Error in is.factor(x): object 'ActorTitles' not found

``` {.r}
ActorTitles<-na.omit(ActorTitles) %>%  group_by(actor)  %>% summarise(count = n()) %>% arrange(desc(count)) %>% top_n(10)
```

    ## Error in na.omit(ActorTitles): object 'ActorTitles' not found

``` {.r}
ActorTitles<-as.data.frame(ActorTitles)
```

    ## Error in as.data.frame(ActorTitles): object 'ActorTitles' not found

``` {.r}
ActorTitles
```

    ## Error in eval(expr, envir, enclos): object 'ActorTitles' not found

``` {.r}
actr_<-ggplot(data=ActorTitles, aes(x=actor, y=count)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label=count), vjust=1.6, color="white", size=5.5)+
  theme_classic()
```

    ## Error in ggplot(data = ActorTitles, aes(x = actor, y = count)): object 'ActorTitles' not found

``` {.r}
actr_
```

    ## Error in eval(expr, envir, enclos): object 'actr_' not found

``` {.r}
##Convert rating to factor level
NetflixDF$rating <- as.numeric(factor(NetflixDF$rating))
```

    ## Error in factor(NetflixDF$rating): object 'NetflixDF' not found

``` {.r}
## "type" and "Listed_in" should be categorical variable
NetflixDF$listed_in <- as.numeric(factor(NetflixDF$listed_in))
```

    ## Error in factor(NetflixDF$listed_in): object 'NetflixDF' not found

``` {.r}
NetflixDF$type <- as.numeric(factor(NetflixDF$type))
```

    ## Error in factor(NetflixDF$type): object 'NetflixDF' not found

``` {.r}
NetflixDF$rating[is.na(NetflixDF$rating)] <- getmode(NetflixDF$rating)
```

    ## Error in unique(v): object 'NetflixDF' not found

``` {.r}
summary(NetflixDF)
```

    ## Error in summary(NetflixDF): object 'NetflixDF' not found

``` {.r}
#install.packages("tm")  # for text mining
#install.packages("SnowballC") # for text stemming
#install.packages("wordcloud") # word-cloud generator 
#install.packages("RColorBrewer") # color palettes
# Load
library("tm")
```

    ## Loading required package: NLP

    ## 
    ## Attaching package: 'NLP'

    ## The following object is masked from 'package:ggplot2':
    ## 
    ##     annotate

``` {.r}
library("SnowballC")
```

    ## Error in library("SnowballC"): there is no package called 'SnowballC'

``` {.r}
library("wordcloud")
```

    ## Error in library("wordcloud"): there is no package called 'wordcloud'

``` {.r}
library("RColorBrewer")

# Load the data as a corpus
Netflixdocs <- Corpus(VectorSource(jointDF$genre))
```

    ## Error in SimpleSource(length = length(x), content = x, class = "VectorSource"): object 'jointDF' not found

``` {.r}
inspect(Netflixdocs)
```

    ## Error in inspect(Netflixdocs): object 'Netflixdocs' not found

``` {.r}
###Text Transformation
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
Netflixdocs <- tm_map(Netflixdocs, toSpace, "/")
```

    ## Error in tm_map(Netflixdocs, toSpace, "/"): object 'Netflixdocs' not found

``` {.r}
Netflixdocs <- tm_map(Netflixdocs, toSpace, "@")
```

    ## Error in tm_map(Netflixdocs, toSpace, "@"): object 'Netflixdocs' not found

``` {.r}
Netflixdocs <- tm_map(Netflixdocs, toSpace, "\\|")
```

    ## Error in tm_map(Netflixdocs, toSpace, "\\|"): object 'Netflixdocs' not found

``` {.r}
###Clean text
# Convert the text to lower case
Netflixdocs <- tm_map(Netflixdocs, content_transformer(tolower))
```

    ## Error in tm_map(Netflixdocs, content_transformer(tolower)): object 'Netflixdocs' not found

``` {.r}
# Remove numbers
Netflixdocs <- tm_map(Netflixdocs, removeNumbers)
```

    ## Error in tm_map(Netflixdocs, removeNumbers): object 'Netflixdocs' not found

``` {.r}
# Remove english common stopwords
Netflixdocs <- tm_map(Netflixdocs, removeWords, stopwords("english"))
```

    ## Error in tm_map(Netflixdocs, removeWords, stopwords("english")): object 'Netflixdocs' not found

``` {.r}
# Remove your own stop word
# specify your stopwords as a character vector
Netflixdocs <- tm_map(Netflixdocs, removeWords, c("blabla1", "blabla2")) 
```

    ## Error in tm_map(Netflixdocs, removeWords, c("blabla1", "blabla2")): object 'Netflixdocs' not found

``` {.r}
# Remove punctuations
Netflixdocs <- tm_map(Netflixdocs, removePunctuation)
```

    ## Error in tm_map(Netflixdocs, removePunctuation): object 'Netflixdocs' not found

``` {.r}
# Eliminate extra white spaces
Netflixdocs <- tm_map(Netflixdocs, stripWhitespace)
```

    ## Error in tm_map(Netflixdocs, stripWhitespace): object 'Netflixdocs' not found

``` {.r}
###create Term document
dtm <- TermDocumentMatrix(Netflixdocs)
```

    ## Error in TermDocumentMatrix(Netflixdocs): object 'Netflixdocs' not found

``` {.r}
m <- as.matrix(dtm)
```

    ## Error in as.matrix(dtm): object 'dtm' not found

``` {.r}
v <- sort(rowSums(m),decreasing=TRUE)
```

    ## Error in is.data.frame(x): object 'm' not found

``` {.r}
dir_ <- data.frame(word = names(v),freq=v)
```

    ## Error in data.frame(word = names(v), freq = v): object 'v' not found

``` {.r}
head(dir_, 10)
```

    ## Error in head(dir_, 10): object 'dir_' not found

``` {.r}
set.seed(05)
wordcloud(words = dir_$word, freq = dir_$freq, min.freq = 1,
          max.words=20, random.order=FALSE, rot.per=0.5, 
          colors=brewer.pal(10, "Dark2"))
```

    ## Error in wordcloud(words = dir_$word, freq = dir_$freq, min.freq = 1, : could not find function "wordcloud"

``` {.r}
##Explore frequent terms and their associations
findFreqTerms(dtm, lowfreq = 4)
```

    ## Error in stopifnot(inherits(x, c("DocumentTermMatrix", "TermDocumentMatrix")), : object 'dtm' not found

``` {.r}
## Analyze the association between frequent terms (i.e., terms which correlate) using findAssocs() function
findAssocs(dtm, terms = "thriller", corlimit = 0.1)
```

    ## Error in findAssocs(dtm, terms = "thriller", corlimit = 0.1): object 'dtm' not found

``` {.r}
library(dplyr)
library(janeaustenr)
```

    ## Error in library(janeaustenr): there is no package called 'janeaustenr'

``` {.r}
library(tidytext)
```

    ## Error in library(tidytext): there is no package called 'tidytext'

``` {.r}
Netflix_words <- jointDF %>%
  unnest_tokens(word, description) %>%
  count(title, word, sort = TRUE)
```

    ## Error in unnest_tokens(., word, description): could not find function "unnest_tokens"

``` {.r}
##netflix-title,description-text

total_words <- Netflix_words %>% group_by(title) %>% summarize(total = sum(n))
```

    ## Error in group_by(., title): object 'Netflix_words' not found

``` {.r}
Netflix_words <- left_join(Netflix_words, total_words)
```

    ## Error in left_join(Netflix_words, total_words): object 'Netflix_words' not found

``` {.r}
Netflix_words
```

    ## Error in eval(expr, envir, enclos): object 'Netflix_words' not found

``` {.r}
 ###Calculating tf-idf attempts to find the words that are important (i.e., common) in a text, but not too common.
###https://cran.r-project.org/web/packages/tidytext/vignettes/tf_idf.html
Netflix_words <- Netflix_words %>%
  bind_tf_idf(word, title, n)
```

    ## Error in bind_tf_idf(., word, title, n): could not find function "bind_tf_idf"

``` {.r}
head(Netflix_words,10)
```

    ## Error in head(Netflix_words, 10): object 'Netflix_words' not found

``` {.r}
Netflix_words %>%
  select(-total) %>%
  arrange(desc(tf_idf))
```

    ## Error in select(., -total): object 'Netflix_words' not found

``` {.r}
Netflix_words %>%
  filter(title == "One Day") %>%
  select(-total) %>%
  arrange(desc(tf_idf))
```

    ## Error in filter(., title == "One Day"): object 'Netflix_words' not found

``` {.r}
#############################################################################################################################

###Columns in the joined data of Netflix and Imdb
colnames(jointDF)
```

    ## Error in is.data.frame(x): object 'jointDF' not found

``` {.r}
Netflix_rating_data<-subset(jointDF, select = c("reviews_from_users","show_id","weighted_average_vote"))
```

    ## Error in subset(jointDF, select = c("reviews_from_users", "show_id", "weighted_average_vote")): object 'jointDF' not found

``` {.r}
Netflix_movie_data<-subset(jointDF, select = c("title","description","show_id","genre"))
```

    ## Error in subset(jointDF, select = c("title", "description", "show_id", : object 'jointDF' not found

``` {.r}
movie_genre <- as.data.frame(Netflix_movie_data$genre, stringsAsFactors=FALSE)
```

    ## Error in as.data.frame(Netflix_movie_data$genre, stringsAsFactors = FALSE): object 'Netflix_movie_data' not found

``` {.r}
movie_genre2 <- as.data.frame(tstrsplit(movie_genre[,1], '[,]', 
                                   type.convert=TRUE), 
                         stringsAsFactors=FALSE) 
```

    ## Error in strsplit(as.character(x), ...): object 'movie_genre' not found

``` {.r}
colnames(movie_genre2) <- c(1:3)
```

    ## Error in colnames(movie_genre2) <- c(1:3): object 'movie_genre2' not found

``` {.r}
list_genre <- c("Action", "Adventure", "Animation", "Children", 
                "Comedy", "Crime","Documentary", "Drama", "Fantasy",
                "Film-Noir", "Horror", "Musical", "Mystery","Romance",
                "Sci-Fi", "Thriller", "War", "Western")

genre_DF1 <- matrix(0,2332,18)
genre_DF1[1,] <- list_genre
colnames(genre_DF1) <- list_genre
for (index in 1:nrow(movie_genre2)) {
  for (col in 1:ncol(movie_genre2)) {
    gen_col = which(genre_DF1[1,] == movie_genre2[index,col]) 
    genre_DF1[index+1,gen_col] <- 1
}
}
```

    ## Error in nrow(movie_genre2): object 'movie_genre2' not found

``` {.r}
genre_DF2 <- as.data.frame(genre_DF1[-1,], stringsAsFactors=FALSE) #remove first row, which was the genre list
for (col in 1:ncol(genre_DF2)) {
  genre_DF2[,col] <- as.integer(genre_DF2[,col]) #convert from characters to integers
} 
str(genre_DF2)
```

    ## 'data.frame':    2331 obs. of  18 variables:
    ##  $ Action     : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Adventure  : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Animation  : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Children   : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Comedy     : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Crime      : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Documentary: int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Drama      : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Fantasy    : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Film-Noir  : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Horror     : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Musical    : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Mystery    : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Romance    : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Sci-Fi     : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Thriller   : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ War        : int  0 0 0 0 0 0 0 0 0 0 ...
    ##  $ Western    : int  0 0 0 0 0 0 0 0 0 0 ...

``` {.r}
Mtrx_Search <- cbind(Netflix_movie_data[,1:2], genre_DF2[])
```

    ## Error in cbind(Netflix_movie_data[, 1:2], genre_DF2[]): object 'Netflix_movie_data' not found

``` {.r}
head(Mtrx_Search)
```

    ## Error in head(Mtrx_Search): object 'Mtrx_Search' not found

``` {.r}
Mtrx_Rating <- dcast(Netflix_rating_data, reviews_from_users~show_id, value.var = "weighted_average_vote", na.rm=FALSE,fun=mean)
```

    ## Error in is.data.table(data): object 'Netflix_rating_data' not found

``` {.r}
##Netflix_rating_data<-subset(jointDF, select = c("reviews_from_users","show_id","weighted_average_vote"


Mtrx_Rating <- as.matrix(Mtrx_Rating[,-1]) #remove userIds/reviews from users
```

    ## Error in as.matrix(Mtrx_Rating[, -1]): object 'Mtrx_Rating' not found

``` {.r}
Mtrx_Rating <- as(Mtrx_Rating, "realRatingMatrix")#Convert rating matrix into a recommenderlab sparse matrix
```

    ## Error in .class1(object): object 'Mtrx_Rating' not found

``` {.r}
Mtrx_Rating
```

    ## Error in eval(expr, envir, enclos): object 'Mtrx_Rating' not found

``` {.r}
recommnd_ml <- recommenderRegistry$get_entries(dataType = "realRatingMatrix")
```

    ## Error in eval(expr, envir, enclos): object 'recommenderRegistry' not found

``` {.r}
names(recommnd_ml)
```

    ## Error in eval(expr, envir, enclos): object 'recommnd_ml' not found

``` {.r}
recommnd_ml$IBCF_realRatingMatrix$parameters
```

    ## Error in eval(expr, envir, enclos): object 'recommnd_ml' not found

``` {.r}
mtrx_similarity <- similarity(Mtrx_Rating[1:4, ],
                               method = "cosine",
                               which = "users")
```

    ## Error in similarity(Mtrx_Rating[1:4, ], method = "cosine", which = "users"): could not find function "similarity"

``` {.r}
as.matrix(mtrx_similarity)
```

    ## Error in as.matrix(mtrx_similarity): object 'mtrx_similarity' not found

``` {.r}
image(as.matrix(mtrx_similarity), main = "User's Similarities")
```

    ## Error in as.matrix(mtrx_similarity): object 'mtrx_similarity' not found

``` {.r}
SImilarityMovie <- similarity(Mtrx_Rating[, 30:40], method =
                                 "cosine", which = "items")
```

    ## Error in similarity(Mtrx_Rating[, 30:40], method = "cosine", which = "items"): could not find function "similarity"

``` {.r}
as.matrix(SImilarityMovie)
```

    ## Error in as.matrix(SImilarityMovie): object 'SImilarityMovie' not found

``` {.r}
image(as.matrix(SImilarityMovie), main = "Movies similarity")
```

    ## Error in as.matrix(SImilarityMovie): object 'SImilarityMovie' not found

``` {.r}
ratingVals <- as.vector(Mtrx_Rating@data)
```

    ## Error in as.vector(Mtrx_Rating@data): object 'Mtrx_Rating' not found

``` {.r}
unique(ratingVals) # extracting unique ratings
```

    ## Error in unique(ratingVals): object 'ratingVals' not found

``` {.r}
Rating_Tbl <- table(ratingVals) # creating a count of movie ratings
```

    ## Error in table(ratingVals): object 'ratingVals' not found

``` {.r}
Rating_Tbl
```

    ## Error in eval(expr, envir, enclos): object 'Rating_Tbl' not found

``` {.r}
RatingMovie <- Mtrx_Rating[rowCounts(Mtrx_Rating) > 1,
                             colCounts(Mtrx_Rating) > 1]
```

    ## Error in eval(expr, envir, enclos): object 'Mtrx_Rating' not found

``` {.r}
RatingMovie
```

    ## Error in eval(expr, envir, enclos): object 'RatingMovie' not found

``` {.r}
DFSampled<- sample(x = c(TRUE, FALSE),
                      size = nrow(RatingMovie),
                      replace = TRUE,
                      prob = c(0.8, 0.2))
```

    ## Error in nrow(RatingMovie): object 'RatingMovie' not found

``` {.r}
trn_DF <- RatingMovie[DFSampled, ]
```

    ## Error in eval(expr, envir, enclos): object 'RatingMovie' not found

``` {.r}
tst_DF <- RatingMovie[!DFSampled, ]
```

    ## Error in eval(expr, envir, enclos): object 'RatingMovie' not found

``` {.r}
recommnd_SM <- recommenderRegistry$get_entries(dataType ="realRatingMatrix")
```

    ## Error in eval(expr, envir, enclos): object 'recommenderRegistry' not found

``` {.r}
recommnd_SM$IBCF_realRatingMatrix$parameters
```

    ## Error in eval(expr, envir, enclos): object 'recommnd_SM' not found

``` {.r}
recommnd_model <- Recommender(data = trn_DF,
                          method = "IBCF",
                          parameter = list(k = 30))
```

    ## Error in Recommender(data = trn_DF, method = "IBCF", parameter = list(k = 30)): could not find function "Recommender"

``` {.r}
recommnd_model
```

    ## Error in eval(expr, envir, enclos): object 'recommnd_model' not found

``` {.r}
class(recommnd_model)
```

    ## Error in eval(expr, envir, enclos): object 'recommnd_model' not found

``` {.r}
infoModel <- getModel(recommnd_model)
```

    ## Error in getModel(recommnd_model): could not find function "getModel"

``` {.r}
class(infoModel$sim)
```

    ## Error in eval(expr, envir, enclos): object 'infoModel' not found

``` {.r}
dim(infoModel$sim)
```

    ## Error in eval(expr, envir, enclos): object 'infoModel' not found

``` {.r}
top_items <- 20

#image(infoModel$sim[1:top_items, 1:top_items],main = "Heatmap of the first rows and columns")

sum_rows <- rowSums(infoModel$sim > 0)
```

    ## Error in is.data.frame(x): object 'infoModel' not found

``` {.r}
table(sum_rows)
```

    ## Error in table(sum_rows): object 'sum_rows' not found

``` {.r}
sum_cols <- colSums(infoModel$sim > 0)
```

    ## Error in is.data.frame(x): object 'infoModel' not found

``` {.r}
qplot(sum_cols, fill=I("steelblue"), col=I("red"))+ ggtitle("Distribution of the column count")
```

    ## Error in eval_tidy(mapping$x, data, caller_env): object 'sum_cols' not found

``` {.r}
TopRecomndtns <- 10 # the number of items to recommend to each user
PredRecomndtns <- predict(object = recommnd_model,
                          newdata = tst_DF,
                          n = TopRecomndtns)
```

    ## Error in predict(object = recommnd_model, newdata = tst_DF, n = TopRecomndtns): object 'recommnd_model' not found

``` {.r}
PredRecomndtns
```

    ## Error in eval(expr, envir, enclos): object 'PredRecomndtns' not found

``` {.r}
user1 <- PredRecomndtns@items[[1]] # recommendation for the first user
```

    ## Error in eval(expr, envir, enclos): object 'PredRecomndtns' not found

``` {.r}
movies_user1 <- PredRecomndtns@itemLabels[user1]
```

    ## Error in eval(expr, envir, enclos): object 'PredRecomndtns' not found

``` {.r}
movies_user2 <- movies_user1
```

    ## Error in eval(expr, envir, enclos): object 'movies_user1' not found

``` {.r}
for (index in 1:10){
  movies_user2[index] <- as.character(subset(Netflix_movie_data,
                                         Netflix_movie_data$show_id== movies_user1[index])$title)
}
```

    ## Error in subset(Netflix_movie_data, Netflix_movie_data$show_id == movies_user1[index]): object 'Netflix_movie_data' not found

``` {.r}
movies_user2
```

    ## Error in eval(expr, envir, enclos): object 'movies_user2' not found

``` {.r}
user10 <- PredRecomndtns@items[[10]] # recommendation for the tenth user
```

    ## Error in eval(expr, envir, enclos): object 'PredRecomndtns' not found

``` {.r}
movies_user1 <- PredRecomndtns@itemLabels[user10]
```

    ## Error in eval(expr, envir, enclos): object 'PredRecomndtns' not found

``` {.r}
movies_user2 <- movies_user1
```

    ## Error in eval(expr, envir, enclos): object 'movies_user1' not found

``` {.r}
for (index in 1:10){
  movies_user2[index] <- as.character(subset(Netflix_movie_data,
                                         Netflix_movie_data$show_id== movies_user1[index])$title)
}
```

    ## Error in subset(Netflix_movie_data, Netflix_movie_data$show_id == movies_user1[index]): object 'Netflix_movie_data' not found

``` {.r}
movies_user2
```

    ## Error in eval(expr, envir, enclos): object 'movies_user2' not found

``` {.r}
recommendation_matrix <- sapply(PredRecomndtns@items,
                      function(x){ as.integer(colnames(RatingMovie)[x]) }) # matrix with the recommendations for each user
```

    ## Error in lapply(X = X, FUN = FUN, ...): object 'PredRecomndtns' not found

``` {.r}
recommendation_matrix[1:10]
```

    ## Error in eval(expr, envir, enclos): object 'recommendation_matrix' not found

``` {.r}
DF<-na.omit(jointDF)
```

    ## Error in na.omit(jointDF): object 'jointDF' not found

``` {.r}
str(DF)
```

    ## Error in str(DF): object 'DF' not found

``` {.r}
DF <- as.data.frame(unclass(jointDF))  ###convert to factor levels
```

    ## Error in as.data.frame(unclass(jointDF)): object 'jointDF' not found

``` {.r}
str(DF)
```

    ## Error in str(DF): object 'DF' not found

``` {.r}
#number of missing values for each variable for NetflixDF
data.frame("variable"=c(colnames(DF)), "missing values"=sapply(DF, function(x) sum(is.na(x))), row.names=NULL)
```

    ## Error in is.data.frame(x): object 'DF' not found

``` {.r}
## when the whole dataset is used for fitting a linear model
movies_model1 = lm(weighted_average_vote ~ rating + genre + director + reviews_from_users + country + listed_in + duration, data = DF,drop.unused.levels = TRUE)
```

    ## Error in is.data.frame(data): object 'DF' not found

``` {.r}
summary(movies_model1)
```

    ## Error in summary(movies_model1): object 'movies_model1' not found

``` {.r}
library (caret) 
```

    ## Loading required package: lattice

``` {.r}
inTrain = createDataPartition (DF[,'weighted_average_vote'], p=0.8, list= FALSE ) 
```

    ## Error in createDataPartition(DF[, "weighted_average_vote"], p = 0.8, list = FALSE): object 'DF' not found

``` {.r}
training = DF[inTrain,] 
```

    ## Error in eval(expr, envir, enclos): object 'DF' not found

``` {.r}
validation = DF[-inTrain,] 
```

    ## Error in eval(expr, envir, enclos): object 'DF' not found

``` {.r}
### When the training set is used for  running the model                
movie.linear = lm(weighted_average_vote ~ rating + genre  + reviews_from_users + country + listed_in + duration,data = training,drop.unused.levels = TRUE)
```

    ## Error in is.data.frame(data): object 'training' not found

``` {.r}
summary(movie.linear )
```

    ## Error in summary(movie.linear): object 'movie.linear' not found

``` {.r}
#predicted.linear = predict(movie.linear, validation)*10


#install.packages("gbm")
library(gbm)
```

    ## Error in library(gbm): there is no package called 'gbm'

``` {.r}
movie.boost=gbm(weighted_average_vote ~ rating + genre  + reviews_from_users + country + listed_in + duration,data = training,distribution="gaussian",n.trees=5000,interaction.depth=4)
```

    ## Error in gbm(weighted_average_vote ~ rating + genre + reviews_from_users + : could not find function "gbm"

``` {.r}
summary(movie.boost)
```

    ## Error in summary(movie.boost): object 'movie.boost' not found

``` {.r}
predicted.boost=predict(movie.boost,newdata=validation,n.trees=5000)
```

    ## Error in predict(movie.boost, newdata = validation, n.trees = 5000): object 'movie.boost' not found

``` {.r}
# calculate the sum of squared error
sum((validation$weighted_average_vote - predicted.boost)^2, na.rm=T)
```

    ## Error in eval(expr, envir, enclos): object 'validation' not found
